Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-07 paper/sections/abstract.tex
[ paper ] minor changes, title and abstract.

\begin{abstract}
In this paper, we describe our approach to reconstruct and verify in
\Agda, a  proof assistant,  solutions obtained by \Metis, an
automatic theorem prover, to problems in classical propositional
logic. The translation method consists of justifying step-by-step
each deduction found in the prover's solution. To carry out this
plan, we emulate the inference rules of the prover, providing a
version of them in the proof assistant. Finally, we parse the output
of the prover,  constructing the respective tree associated with the
proof, ending up with an \Agda code for type-checking.

>>>>

\begin{abstract}
In this paper, we describe our approach to reconstruct and verify in
\Agda, a  proof assistant, solutions obtained by \Metis, an
automatic theorem prover, to problems in classical propositional
logic. The translation method consists of justifying step-by-step
each deduction found in the prover's solution. To carry out this
plan, we emulate the inference rules of the prover, providing a
version of them in the proof assistant. Finally, we parse the output
of the prover, constructing the respective tree associated with the
proof, for ending up with an \Agda code for type-checking.
